Array

### 2013-12-03 PAPERS/Report/AdvancedTypes/AdvancedTypes.tex
Adding the first notes about record/structure

       \begin{tabular}[t]{rcl}   
        \hline
        \multicolumn{3}{|c|}{Variable declaration: \B{VarD}} \\
        \hline
        \B{vars} & : & seq \B{Name} \\
        \B{body} & : & seq \B{Inst} \\
  	\hline
        \multicolumn{3}{|c|}{If: \B{If}} \\
        \hline
        \B{branches} & : & seq \B{IfBr} \\
        \hline
        \multicolumn{3}{|c|}{Becomes equal: \B{Beq}} \\
        \hline
        \B{lhs} & : & \B{LValue} \\
        \B{rhs} & : & \B{Expr} \\
	\hline
	\multicolumn{3}{|c|}{Label value: \B{LValue}} \\	
	\hline
	\multicolumn{3}{c}{ \B{Vari} \alt \B{ArrayItem} }\\
        \hline
        \multicolumn{3}{|c|}{Operation call: \B{Call}} \\
        \hline
        \B{op} & : & \B{Oper} \\
        \B{inp} & : & seq \B{Expr} \\
        \B{out} & : & seq \B{Name} \\
        \B{inst} & : & opt \B{Impo} \\
        \hline
        \multicolumn{3}{|c|}{Case conditional: \B{Case}} \\
        \hline
        \B{expr} & : & \B{Expr} \\
        \B{branches} & : & seq \B{CaseBr}\\
	\hline
        \multicolumn{3}{|c|}{Case branch: \B{CaseBr}} \\
        \hline
        \B{val} & : & seq \B{Value} \\
        \B{body} & : & \B{Inst}
        \\
        \hline
        \multicolumn{3}{|c|}{While loop: \B{While}} \\
        \hline
        \B{cond} & : & \B{Pred} \\
        \B{body} & : & \B{Inst} \\
        \hline
        \multicolumn{3}{|c|}{If branch: \B{IfBr}} \\
        \hline
        \B{cond} & : & opt \B{Pred} \\
        \B{body} & : & \B{Inst} \\
        \hline
        \multicolumn{3}{|c|}{Expression: \B{Expr}} \\
        \hline
        \multicolumn{3}{c} {\B{Lit} \alt \B{Term} \alt \B{Pred} \alt \B{Cons}}\\
	\multicolumn{3}{c} {\B{Vari} \alt \B{Array} \alt \B{ArrayItem} } \\
        \hline
        \multicolumn{3}{|c|}{Term expression: \B{Term}} \\
        \hline
        \B{op} & : & \B{ArithOp} \\
        \B{args} & : & seq \B{Exp} \\
  \end{tabular}

  \begin{tabular}[t]{rcl}
	\hline
        \multicolumn{3}{|c|}{Predicate: \B{Pred}} \\
        \hline
        \multicolumn{3}{c}{\B{Form} \alt \B{Comp}} \\
        \hline
        \multicolumn{3}{|c|}{Boolean formula: \B{Form}} \\
        \hline
        \B{op} & : & \B{BoolOp} \\
        \B{args} & : & seq \B{Pred} \\
        \hline
        \multicolumn{3}{|c|}{Comparison: \B{Comp}} \\
        \hline
        \B{op} & : & \B{RelOp} \\
        \B{arg1}, \B{arg2} & : & \B{Exp} \\
        \hline
        \multicolumn{3}{|c|}{Data type: \B{Type}} \\
        \hline
        \multicolumn{3}{c}{\B{INT} \alt \B{BOOL}\alt \B{ArrayType}}\\
	\hline	
        \multicolumn{3}{|c|}{Array type : \B{ArrayType}} \\
        \hline 
	\B{dom} & : & seq \B{Set}\\
	\B{ran} & : & \B{Set}\\
        \hline
        \multicolumn{3}{|c|}{Array expression : \B{Array}} \\
        \hline
	\multicolumn{3}{c}{ seq \B{Map} \alt \B{Product} }\\
	\hline
  	\multicolumn{3}{|c|}{Ordered pair : \B{Map}} \\
        \hline
	\B{arg1} & : & seq \B{Expr}\\ 
	\B{arg2} & : & \B{Expr}\\ 
	\hline
  	\multicolumn{3}{|c|}{Cartesian product : \B{Product}} \\
        \hline
	\B{arg1} & : & seq \B{Expr}\\ 
	\B{arg2} & : & \B{Expr}\\ 	
	\hline
	\multicolumn{3}{|c|}{Access array : \B{ArrayItem}} \\
        \hline
	\B{base} & : &  \B{Array} \\
	\B{indices} & : & seq \B{Expr}\\
	\B{type} & : & \B{ArrayType}\\
	\hline
	\multicolumn{3}{|c|}{Simple set : \B{Set}} \\
	\hline
	\multicolumn{3}{c}{\B{BOOL} \alt \B{NAT} \alt \B{NAT$_{1}$}\alt } \\
	\multicolumn{3}{c}{\B{INT} \alt \B{Interval}} \\
	\hline
	\multicolumn{3}{|c|}{B0 interval : \B{Interval}} \\
	\hline
	\B{start}, \B{end} & : & \B{Expr} \\
	\hline
	\multicolumn{3}{|c|}{Literal : \B{Lit}} \\
	\hline
	\multicolumn{3}{c}{ \B{Bool\_lit} \alt \B{Int\_lit}} \\ 
      \end{tabular}
    \end{tabular}
  }
  }
    \caption{Abstract syntax structure of a B implementation.  For each abstract
      syntax element, we give the name of the class (e.g. \B{CaseBr} for a
      branch in a case instruction, and the different attributes of the class),
      or a list of the possible sub-classes (e.g. \B{Inst} for the different
      kinds of instructions).
      Sequence and optional attributes are denoted ``seq'' and ``opt'',
      respectively}
    \label{tab:node-attr}
  \end{center}
\end{figure}

@@

\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
 array := array2;
 structure1 := structure2;
\end{minted}

\subsubsection{Issues and problems}
\begin{itemize}
	\item To develop support to structures (more easy)
	\item To integrate it in translation.tex
\end{itemize}

@@

>>>>

       \begin{tabular}[t]{rcl}   
        \hline
        \multicolumn{3}{|c|}{Variable declaration: \B{VarD}} \\
        \hline
        \B{vars} & : & seq \B{Name} \\
        \B{body} & : & seq \B{Inst} \\
  	\hline
        \multicolumn{3}{|c|}{If: \B{If}} \\
        \hline
        \B{branches} & : & seq \B{IfBr} \\
        \hline
        \multicolumn{3}{|c|}{Becomes equal: \B{Beq}} \\
        \hline
        \B{lhs} & : & \B{LValue} \\
        \B{rhs} & : & \B{Expr} \\
	\hline
	\multicolumn{3}{|c|}{Label value: \B{LValue}} \\	
	\hline
	\multicolumn{3}{c}{ \B{Vari} \alt \B{ArrayItem} }\\
        \hline
        \multicolumn{3}{|c|}{Operation call: \B{Call}} \\
        \hline
        \B{op} & : & \B{Oper} \\
        \B{inp} & : & seq \B{Expr} \\
        \B{out} & : & seq \B{Name} \\
        \B{inst} & : & opt \B{Impo} \\
        \hline
        \multicolumn{3}{|c|}{Case conditional: \B{Case}} \\
        \hline
        \B{expr} & : & \B{Expr} \\
        \B{branches} & : & seq \B{CaseBr}\\
	\hline
        \multicolumn{3}{|c|}{Case branch: \B{CaseBr}} \\
        \hline
        \B{val} & : & seq \B{Value} \\
        \B{body} & : & \B{Inst}
        \\
        \hline
        \multicolumn{3}{|c|}{While loop: \B{While}} \\
        \hline
        \B{cond} & : & \B{Pred} \\
        \B{body} & : & \B{Inst} \\
        \hline
        \multicolumn{3}{|c|}{If branch: \B{IfBr}} \\
        \hline
        \B{cond} & : & opt \B{Pred} \\
        \B{body} & : & \B{Inst} \\
        \hline
        \multicolumn{3}{|c|}{Expression: \B{Expr}} \\
        \hline
        \multicolumn{3}{c} {\B{Lit} \alt \B{Term} \alt \B{Pred} \alt \B{Cons}}\\
	\multicolumn{3}{c} {\B{Vari} \alt \B{Array} \alt \B{ArrayItem} } \\
        \hline
        \multicolumn{3}{|c|}{Term expression: \B{Term}} \\
        \hline
        \B{op} & : & \B{ArithOp} \\
        \B{args} & : & seq \B{Exp} \\
	\hline
        \multicolumn{3}{|c|}{Predicate: \B{Pred}} \\
        \hline
        \multicolumn{3}{c}{\B{Form} \alt \B{Comp}} \\
\end{tabular}

  \begin{tabular}[t]{rcl}
	\hline
        \multicolumn{3}{|c|}{Boolean formula: \B{Form}} \\
        \hline
        \B{op} & : & \B{BoolOp} \\
        \B{args} & : & seq \B{Pred} \\
        \hline
        \multicolumn{3}{|c|}{Comparison: \B{Comp}} \\
        \hline
        \B{op} & : & \B{RelOp} \\
        \B{arg1}, \B{arg2} & : & \B{Exp} \\
        \hline
        \multicolumn{3}{|c|}{Data type: \B{Type}} \\
        \hline
        \multicolumn{3}{c}{\B{INT} \alt \B{BOOL}\alt}\\
	\multicolumn{3}{c}{\B{Struct} \alt \B{ArrayType}}\\
	\hline
  	\multicolumn{3}{|c|}{Data structure : \B{Struct}} \\
        \hline
	\B{id} & : &  \B{Name}\\
        \B{elements} & : & seq \B{Name} \\
	\B{type} & : & seq \B{Type}\\
	\hline
%  	\multicolumn{3}{|c|}{Data record : \B{Record}} \\
%        \hline
%	\B{id} & : &  \B{Name}\\
%        \B{elements} & : & seq \B{Name} \\
%	\B{type} & : & \B{Struct}\\
%	\hline
        \multicolumn{3}{|c|}{Array type : \B{ArrayType}} \\
        \hline 
	\B{dom} & : & seq \B{Set}\\
	\B{ran} & : & \B{Set}\\
        \hline
        \multicolumn{3}{|c|}{Array expression : \B{Array}} \\
        \hline
	\multicolumn{3}{c}{ seq \B{Map} \alt \B{Product} }\\
	\hline
  	\multicolumn{3}{|c|}{Ordered pair : \B{Map}} \\
        \hline
	\B{arg1} & : & seq \B{Expr}\\ 
	\B{arg2} & : & \B{Expr}\\ 
	\hline
  	\multicolumn{3}{|c|}{Cartesian product : \B{Product}} \\
        \hline
	\B{arg1} & : & seq \B{Expr}\\ 
	\B{arg2} & : & \B{Expr}\\ 	
	\hline
	\multicolumn{3}{|c|}{Access array : \B{ArrayItem}} \\
        \hline
	\B{base} & : &  \B{Array} \\
	\B{indices} & : & seq \B{Expr}\\
	\B{type} & : & \B{ArrayType}\\
	\hline
	\multicolumn{3}{|c|}{Simple set : \B{Set}} \\
	\hline
	\multicolumn{3}{c}{\B{BOOL} \alt \B{NAT} \alt \B{NAT$_{1}$}\alt } \\
	\multicolumn{3}{c}{\B{INT} \alt \B{Interval}} \\
	\hline
	\multicolumn{3}{|c|}{B0 interval : \B{Interval}} \\
	\hline
	\B{start}, \B{end} & : & \B{Expr} \\
	\hline
	\multicolumn{3}{|c|}{Literal : \B{Lit}} \\
	\hline
	\multicolumn{3}{c}{ \B{Bool\_lit} \alt \B{Int\_lit}} \\ 
      \end{tabular}
    \end{tabular}
  }
  }
    \caption{Abstract syntax structure of a B implementation.  For each abstract
      syntax element, we give the name of the class (e.g. \B{CaseBr} for a
      branch in a case instruction, and the different attributes of the class),
      or a list of the possible sub-classes (e.g. \B{Inst} for the different
      kinds of instructions).
      Sequence and optional attributes are denoted ``seq'' and ``opt'',
      respectively}
    \label{tab:node-attr}
  \end{center}
\end{figure}

@@

\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
 array1 := array2;
 structure1 := structure2;
\end{minted}

@@

This code stores a value in the record and get the value of element.
%TODO example getting
\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}

%TODO example setting
